### 2014-03-04 Abstr.tex
added Abstr.tex

Various MHD equilibrium tools, some of which being recently developped or updated, are used on the medium-size COMPASS tokamak. MHD equilibrium is a fundamental property of the tokamak plasma. Its knowledge is required for many diagnostics and modelling tools. Proper benchmarking and validation of equilibrium tools is thus key for interpretting and plannig tokamak experiments. We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE [?], and the rapid plasma boundary reconstruction part of the EQUINOX code [?]. We demonstrate that FREEBIE can determine the equilibrium and corresponding poloidal field (PF) coils currents from a given plasma boundary. Both EFIT++ and EQUINOX can reconstruct the equilibrium from synthetic diagnostic data (with an artificial noise) from FREEBIE. The accuracy of the reconstruction depends on the noise level and certain numerical parameters. For example, EFIT++ reconstruction with a low-order $p'$ is not perfect

### 2014-03-10 Abstract.tex
renamed Abstr.tex to Abstract.tex
edited Abstract.tex

--- 2014-03-04 Abstr.tex
@@
-Various MHD equilibrium tools, some of which being recently developped or updated, are used on the medium-size COMPASS tokamak.
+\section{Abstract}
+
+Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
 MHD equilibrium is a fundamental property of the tokamak plasma.
@@
 We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE [?], and the rapid plasma boundary reconstruction part of the EQUINOX code [?].
-We demonstrate that FREEBIE can determine the equilibrium and corresponding poloidal field (PF) coils currents from a given plasma boundary.
+We demonstrate that FREEBIE can determine the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.
 Both EFIT++ and EQUINOX can reconstruct the equilibrium from synthetic diagnostic data (with an artificial noise) from FREEBIE.
+Optimum reconstruction parameters are estimated; in addition, possible enhancements using more diagnostics are discussed and simulated using synthetic diagnostics.
+
 The accuracy of the reconstruction depends on the noise level and certain numerical parameters.
-For example, EFIT++ reconstruction with a low-order $p'$ is not perfect
+For example, EFIT++ reconstruction with a low-order $p'\left(\psi\right)$ and $ff'\left(\psi\right)$ is not perfect even with no noise.
+The recent EFIT++ version 6 is several times faster compared to version 4.

### 2014-03-10 Abstract.tex
edited Abstract.tex

@@
 
-Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
+Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or updated, are used on the medium-size COMPASS tokamak \cite{doi:10.1007/s10582-006-0188-1}.
 MHD equilibrium is a fundamental property of the tokamak plasma.

### 2014-03-10 Abstract.tex
edited Abstract.tex

--- 2014-03-10 Abstract.tex
@@
 
-Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
-MHD equilibrium is a fundamental property of the tokamak plasma.
-Its knowledge is required for many diagnostics and modelling tools.
+Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or considerably updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
+MHD equilibrium is a fundamental property of the tokamak plasma, whose knowledge is required for many diagnostics and modelling tools.
 Proper benchmarking and validation of equilibrium tools is thus key for interpretting and plannig tokamak experiments.
-We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE [?], and the rapid plasma boundary reconstruction part of the EQUINOX code [?].
+We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE [?], and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{doi:10.1016/j.jcp.2011.04.005}.
 We demonstrate that FREEBIE can determine the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.

### 2014-03-10 Abstract.tex
edited Abstract.tex

@@
 We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE [?], and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{doi:10.1016/j.jcp.2011.04.005}.
-We demonstrate that FREEBIE can determine the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.
-Both EFIT++ and EQUINOX can reconstruct the equilibrium from synthetic diagnostic data (with an artificial noise) from FREEBIE.
+We demonstrate that FREEBIE can calculate the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.
+Both EFIT++ and EQUINOX can reconstruct equilibria generated by FREEBIE from synthetic diagnostic data (including an artificial noise).
 Optimum reconstruction parameters are estimated; in addition, possible enhancements using more diagnostics are discussed and simulated using synthetic diagnostics.
+FREEBIE can also calculate the temporal evolution of the poloidal field coils currents for a whole plasma scenario.
 

### 2014-03-10 Abstract.tex
deleted the extra text

@@
 FREEBIE can also calculate the temporal evolution of the poloidal field coils currents for a whole plasma scenario.
-
-The accuracy of the reconstruction depends on the noise level and certain numerical parameters.
-For example, EFIT++ reconstruction with a low-order $p'\left(\psi\right)$ and $ff'\left(\psi\right)$ is not perfect even with no noise.
-The recent EFIT++ version 6 is several times faster compared to version 4.

### 2014-03-10 Abstract.tex
edited Abstract.tex

@@
 
-Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or considerably updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
+Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or considerably updated, are used on the medium-size COMPASS tokamak \cite{doi:10.1007/s10582-006-0188-1}.
 MHD equilibrium is a fundamental property of the tokamak plasma, whose knowledge is required for many diagnostics and modelling tools.

### 2014-03-11 Abstract.tex
edited Abstract.tex

@@
 Proper benchmarking and validation of equilibrium tools is thus key for interpretting and plannig tokamak experiments.
-We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE [?], and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{doi:10.1016/j.jcp.2011.04.005}.
+We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE \cite{freebie2012}, and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{doi:10.1016/j.jcp.2011.04.005}.
 We demonstrate that FREEBIE can calculate the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.

### 2014-03-11 Abstract.tex
added missing citations

--- 2014-03-10 Abstract.tex
@@
 Proper benchmarking and validation of equilibrium tools is thus key for interpretting and plannig tokamak experiments.
-We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE [?], and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{doi:10.1016/j.jcp.2011.04.005}.
+We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE \cite{freebie2012}, and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{Blum_2012}.
 We demonstrate that FREEBIE can calculate the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.

### 2014-03-11 Abstract.tex
edited Abstract.tex

@@
 Proper benchmarking and validation of equilibrium tools is thus key for interpretting and plannig tokamak experiments.
-We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [?], the free-boundary equilibrium code FREEBIE \cite{freebie2012}, and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{Blum_2012}.
+We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [L.C.
+Appel et al., to be submitted to Nucl.
+Fusion], the free-boundary equilibrium code FREEBIE \cite{freebie2012}, and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{Blum_2012}.
 We demonstrate that FREEBIE can calculate the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.

### 2014-03-11 Abstract.tex
edited Abstract.tex

@@
 
-Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developped or considerably updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
+Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developed or considerably updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
 MHD equilibrium is a fundamental property of the tokamak plasma, whose knowledge is required for many diagnostics and modelling tools.
-Proper benchmarking and validation of equilibrium tools is thus key for interpretting and plannig tokamak experiments.
+Proper benchmarking and validation of equilibrium tools is thus key for interpreting and planning tokamak experiments.
 We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [L.C.

### 2014-03-13 Abstract.tex
edited Abstract.tex

@@
 
-Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developed or considerably updated, are used on the medium-size COMPASS tokamak \cite{P_nek_2006}.
+Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developed or considerably updated, are used on the medium-size COMPASS tokamak [R.
+Pánek et al., Czech J Phys 56, B125, 2006].
 MHD equilibrium is a fundamental property of the tokamak plasma, whose knowledge is required for many diagnostics and modelling tools.
@@
 Appel et al., to be submitted to Nucl.
-Fusion], the free-boundary equilibrium code FREEBIE \cite{freebie2012}, and the rapid plasma boundary reconstruction part of the EQUINOX code \cite{Blum_2012}.
+Fusion], the free-boundary equilibrium code FREEBIE  [J.-F.
+Artaud, S.H.
+Kim, EPS 2012, P4.023], and a rapid plasma boundary reconstruction code VacTH [B.
+Faugeras et al., PPCF 2014, accepted].
 We demonstrate that FREEBIE can calculate the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.
-Both EFIT++ and EQUINOX can reconstruct equilibria generated by FREEBIE from synthetic diagnostic data (including an artificial noise).
+Both EFIT++ and VacTH can reconstruct equilibria generated by FREEBIE from synthetic diagnostic data (including an artificial noise) and hence might be suitable for real-time control.
 Optimum reconstruction parameters are estimated; in addition, possible enhancements using more diagnostics are discussed and simulated using synthetic diagnostics.

### 2014-09-07 Introduction.tex
minor lean up

\section{Introduction} % (fold)
\label{sec:introduction}

This is intro

% section introduction (end)

### 2014-09-07 Introduction.tex
Some Introduction

@@
+%!TEX root = JUrban_SOFT2014.tex
+
 \section{Introduction} % (fold)
@@
 
-This is intro
+We report here on validation and verification of tokamak equilibrium tools used for the COMPASS tokamak.
+We particularly focus on fundamental global plasma parameters and the shapes of magnetic flux surfaces, which are crucial in diagnostics interpretation and other analyses.
+EFIT++ \cite{efitpp2006} is used for routine equilibrium reconstruction on COMPASS.
+FREEBIE \cite{freebie2012} is a recent free-boundary equilibrium code; FREEBIE enables predictive equilibrium calculation consistent with the poloidal field (PF) components of the tokamak.
+In this study, FREEBIE is used in the so-called inverse mode, which predicts PF coils currents from a give plasma boundary and profiles.
+The third code employed in this study is VacTH \cite{vacthref}, which provides a fast reconstruction of the plasma boundary from magnetic measurements using a toroidal harmonics basis.
+
+In order to verify and validate the aforementioned tolls, we analyse EFIT++ and VacTH reconstructions of equilibria constructed with FREEBIE.
+Synthetic diagnostics (e.g., magnetic probes or flux loops) with optional artificial errors provide inputs for the reconstructions.
 

### 2014-09-07 Procedure.tex
Some Introduction

%!TEX root = JUrban_SOFT2014.tex

\section{Verification and validation procedure} % (fold)
\label{sec:procedure}

% section procedure (end)

### 2014-09-07 Procedure.tex
Something in Procedure

@@
 
+Reliable MHD equilibrium reconstruction is very important for tokamak exploitation.
+Numerous diagnostics and subsequent analyses require as inputs equilibrium properties such as flux surface geometry, magnetic field, stored energy, internal inductance etc.
+We have set up a set of benchmarking tasks, which verify and validate equilibrium tools that are currently employed on COMPASS.
+The procedure is fundamentally following:
+
+\begin{enumerate}
+	\item Equilibrium reconstruction of selected experimental cases using EFIT++.
+	\item Recalculate the equilibria using FREEBIE in inverse mode.
+	\item Optionally alter the equilibria in FREEBIE using e.g. experimental pressure profiles.
+	\item Reconstruct FREEBIE equilibria using EFIT++ and VacTH with various parameters and artificial input noise.
+\end{enumerate}
+
+The first step employs a routine EFIT++ set-up for COMPASS with heuristically tuned parameters.
+In addition to the total plasma current $I_\mathrm{p}$ and the currents in individual PF circuits, 16 partial Rogowski coils and 4 flux loops are employed in this reconstruction and $p'$ and $FF'$ are assumed to be linear functions of the poloidal flux $\psi$.
+FREEBIE inputs $I_\mathrm{p}$, $p'\left( {\bar \psi } \right)$ and $FF'\left( {\bar \psi } \right)$ profiles, the plasma boundary coordinates and an initial guess for the PF coils currents.
+Here, $p$ is the plasma pressure, $F = RB_\phi$ and $\bar\psi$ is the normalized poloidal magnetic flux ($\bar\psi = 0$ on the magnetic axis and $\bar\psi = 1$ on the plasma boundary).
+FREEBIE then seeks a solution to the Grad-Shafranov equation, including the PF coils currents, which minimizes the given plasma shape constraint.
+(This regime is called inverse mode.) FREEBIE can naturally output arbitrary synthetic diagnostics.
+We use here additional 24 poloidally and 24 radially oriented partial Rogowski coils (which are actually mounted on COMPASS) and an artificial set of 16 flux loops located at the same positions as the basic magnetic probes.
+
 % section procedure (end)

### 2014-09-08 Procedure.tex
Text in Procedure. Results.tex added to the layout.

@@
 In addition to the total plasma current $I_\mathrm{p}$ and the currents in individual PF circuits, 16 partial Rogowski coils and 4 flux loops are employed in this reconstruction and $p'$ and $FF'$ are assumed to be linear functions of the poloidal flux $\psi$.
-FREEBIE inputs $I_\mathrm{p}$, $p'\left( {\bar \psi } \right)$ and $FF'\left( {\bar \psi } \right)$ profiles, the plasma boundary coordinates and an initial guess for the PF coils currents.
+In the second step, FREEBIE inputs $I_\mathrm{p}$, $p'\left( {\bar \psi } \right)$ and $FF'\left( {\bar \psi } \right)$ profiles, the plasma boundary coordinates and an initial guess for the PF coils currents.
 Here, $p$ is the plasma pressure, $F = RB_\phi$ and $\bar\psi$ is the normalized poloidal magnetic flux ($\bar\psi = 0$ on the magnetic axis and $\bar\psi = 1$ on the plasma boundary).
+$p'$ comes either from the EFIT++ reconstruction or from Thomson scattering pressure profile $p_\mathrm{TS} = 1.3 n_\mathrm{e} p_\mathrm{e}$.
 FREEBIE then seeks a solution to the Grad-Shafranov equation, including the PF coils currents, which minimizes the given plasma shape constraint.
-(This regime is called inverse mode.) FREEBIE can naturally output arbitrary synthetic diagnostics.
+(This regime is called the inverse mode.) FREEBIE can naturally output arbitrary synthetic diagnostics.
 We use here additional 24 poloidally and 24 radially oriented partial Rogowski coils (which are actually mounted on COMPASS) and an artificial set of 16 flux loops located at the same positions as the basic magnetic probes.
+In the optional third step, an artificial random noise is added to the calculated values of $I_\mathrm{p}$, magnetic probes and flux loops.
+In particular, for a given noise level $l$, $\tilde X = \left( {1 + U\left( { - l,l} \right)^\mathrm{T}} \right)X$, where $X$ is a row vector of the synthetic diagnostics data and $U\left( { - l,l} \right)$ is a random vector of the same shape as $X$ with a uniform distribution on $\left( { - l,l} \right)$.
+
+The final fourth step consists of reconstructing the equilibria form synthetic FREEBIE data using EFIT++ and VacTH.
+The reconstructions are then compared to the original equilibrium, focusing on global parameters and geometry.
+VacTH does not provide a full equilibrium but the plasma shape only; The target of VacTH is to provide such reconstructions in real time for a feedback control.
+Scans are performed over noise levels and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ and the number of harmonics ($n^{\mathrm e}$, $n^{\mathrm p}$) in VacTH.
+Following quantities are used for the comparison.
+\begin{table}[!h]
+    \begin{tabular}{ll}
+    $R_{\mathrm ax}$, $Z_{\mathrm ax}$ & $R,Z$ coordinates of the magnetic axis \\
+    $R_{\mathrm in}$, $R_{\mathrm out}$ & inner/outer $R$ coordinate of LCFS at $Z=Z_{\mathrm ax}$ \\
+    $Z_{\mathrm min}$, $Z_{\mathrm max}$ & minimum/maximum $Z$ coordinate of LCFS \\
+    $\kappa  = \frac{\left( {{Z_{{\rm{max}}}} - {Z_{{\rm{min}}}}} \right) } { \left( {{R_{{\rm{out}}}} - {R_{{\rm{in}}}}} \right) }$          & elongation   \\
+    ${l_{\rm{i}}} = {{\bar B_{\rm{p}}^2}} / {{B_{\rm{a}}^2}}$          & normalized internal inductance   \\
+    ${\beta _{\rm{p}}} = {{2{\mu _0}\bar p}} / {{B_{\rm{a}}^2}}$          & poloidal beta   \\
+    $ W = \int_0^V {3/2p{\rm{d}}V'}$ & stored plasma energy \\
+    $ q_0$, $q_{95}$ & safety factor at $\bar \psi = 0,\ 0.95$ \\
+    \end{tabular}
+\end{table}
+
+Here, $\bar x = \int_0^V {x/V{\rm{d}}V'} $ is a volume average, $V$ is the total plasma volume, $B_{\mathrm a} = \mu _0 I_\mathrm{p} / l_{\mathrm a}$, $l_{\mathrm a}$ is the poloidal LCFS perimeter.
 

### 2014-09-08 Results.tex
Text in Procedure. Results.tex added to the layout.

%!TEX root = JUrban_SOFT2014.tex

\section{Results} % (fold)
\label{sec:results}

% section results (end)

### 2014-09-08 Introduction.tex
Something in Procedure
4275 results

@@
 
-We report here on validation and verification of tokamak equilibrium tools used for the COMPASS tokamak.
+We report here on validation and verification of tokamak equilibrium tools used for the COMPASS tokamak \cite{compass2006}.
 We particularly focus on fundamental global plasma parameters and the shapes of magnetic flux surfaces, which are crucial in diagnostics interpretation and other analyses.
@@
 
-In order to verify and validate the aforementioned tolls, we analyse EFIT++ and VacTH reconstructions of equilibria constructed with FREEBIE.
+In order to verify and validate the aforementioned tools, we analyse EFIT++ and VacTH reconstructions of equilibria constructed with FREEBIE.
 Synthetic diagnostics (e.g., magnetic probes or flux loops) with optional artificial errors provide inputs for the reconstructions.

### 2014-09-08 Procedure.tex
4275 results

@@
 We use here additional 24 poloidally and 24 radially oriented partial Rogowski coils (which are actually mounted on COMPASS) and an artificial set of 16 flux loops located at the same positions as the basic magnetic probes.
+Hereafter, the number of magnetic probes and flux loops are denoted $n_\mathrm{mp}$ and $n_\mathrm{fl}$.
+$n_\mathrm{mp}=16$, $n_\mathrm{fl}=4$ refers the basic set of magnetic measurements, $n_\mathrm{mp}=64$ refers to a set of all presently mounted partial Rogowski coils on COMPASS and $n_\mathrm{fl}=16$ implies artificial flux loops positioned at the same locations as the basic magnetic probes.
 In the optional third step, an artificial random noise is added to the calculated values of $I_\mathrm{p}$, magnetic probes and flux loops.
@@
 The reconstructions are then compared to the original equilibrium, focusing on global parameters and geometry.
-VacTH does not provide a full equilibrium but the plasma shape only; The target of VacTH is to provide such reconstructions in real time for a feedback control.
-Scans are performed over noise levels and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ and the number of harmonics ($n^{\mathrm e}$, $n^{\mathrm p}$) in VacTH.
-Following quantities are used for the comparison.
+VacTH does not provide a full equilibrium but the plasma shape only (the target of VacTH is to provide such reconstructions in real time for a feedback control).
+Scans are performed over noise levels ($\epsilon$) and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ ($n_{p'}$, $n_{FF'}$) and the number of harmonics ($n_{\mathrm p}$, $n_{\mathrm q}$) in VacTH.
+The following quantities are used for the comparison.
 \begin{table}[!h]
@@
     ${\beta _{\rm{p}}} = {{2{\mu _0}\bar p}} / {{B_{\rm{a}}^2}}$          & poloidal beta   \\
-    $ W = \int_0^V {3/2p{\rm{d}}V'}$ & stored plasma energy \\
+    $ W = \int_0^V {\frac{3}{2}p{\rm{d}}V'}$ & stored plasma energy \\
     $ q_0$, $q_{95}$ & safety factor at $\bar \psi = 0,\ 0.95$ \\

### 2014-09-08 Results.tex
4275 results

@@
 
+We have selected five time slices from COMPAS shots 4275 and 6962 (i.e.
+10 cases in total) for the analysis.
+These cases include circular, elongated and diverted plasmas with different currents.
+A comparison of plasma shapes for shot 4275 is shown in Fig.
+\ref{fig:ex4275}.
+Numerical values of reconstruction errors are presented in Table \ref{table:ex4275}.
+We can observe a very good agreement between the original equilibrium and the reconstructed shapes.
+In this case, FREEBIE was using linear $p'$ and $FF'$ polynomials so that the EFIT++ model agrees with the target data.
+VacTH uses 8 magnetic probes and 16 flux loops.
+As we discuss later, flux loops are essential for reliable VacTH results.
+Even global kinetic properties are well reconstructed in EFIT++; the largest error around 10~\% is in $l_{\mathrm i}$ (i.e.
+basically in the toroidal current density profile).
+
+\begin{table*}
+\centering
+
+\begin{tabular}{lrrrrrrrrrrrrr}
+\toprule
+   code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
+\midrule
+ EFIT++ &  0.97 &              0 &            0.002 &        0.001 &        0.001 &                  0.003 &       0.001 &      0.0009 &          0.04 &           0.09 &              0.03 &           0.03 &           0.007 \\
+ EFIT++ &  0.99 &          4e-05 &            9e-05 &        0.001 &        0.001 &                  0.004 &       0.001 &      0.0006 &          0.04 &           0.09 &              0.04 &           0.02 &           0.005 \\
+ EFIT++ &  1.02 &         0.0005 &           0.0002 &        0.002 &        0.002 &                  0.008 &       0.002 &       0.002 &          0.02 &            0.1 &              0.02 &           0.02 &           0.009 \\
+ EFIT++ &  1.05 &          0.001 &           0.0008 &        4e-05 &       0.0003 &                  0.004 &       0.003 &       0.005 &          0.01 &           0.07 &              0.02 &           0.01 &           0.009 \\
+ EFIT++ &   1.1 &          0.001 &           0.0005 &        0.005 &       0.0002 &                  0.005 &       0.004 &       0.002 &          0.04 &           0.09 &              0.03 &           0.02 &            0.05 \\
+  VacTH &  0.97 &              0 &            0.001 &       0.0006 &       0.0002 &                  0.002 &       8e-07 &       7e-05 &           nan &            nan &               nan &            nan &             nan \\
+  VacTH &  0.99 &          4e-05 &           0.0004 &        0.001 &       0.0008 &                  0.004 &       4e-07 &      0.0001 &           nan &            nan &               nan &            nan &             nan \\
+  VacTH &  1.02 &          0.002 &           0.0008 &        0.005 &        0.002 &                   0.01 &       2e-06 &       0.002 &           nan &            nan &               nan &            nan &             nan \\
+  VacTH &  1.05 &          0.006 &            0.002 &        5e-05 &        0.002 &                   0.01 &       3e-06 &        0.02 &           nan &            nan &               nan &            nan &             nan \\
+  VacTH &   1.1 &          0.005 &            0.002 &        0.002 &        0.003 &                   0.02 &       2e-06 &       0.003 &           nan &            nan &               nan &            nan &             nan \\
+\bottomrule
+\end{tabular}
+
+\caption{Errors for the same cases as in Fig. \ref{fig:ex4275}.}
+\label{table:ex4275}
+\end{table*}
+
+\begin{figure*}
+\centering   %\begin{center}
+\hfill{}
+\includegraphics[width=18cm]{figures/example_4275.pdf}
+\hfill{}
+%\end{center}
+\caption{Contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 4275.
+EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
+VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_{\mathrm p} = n_{\mathrm q} = 5$.}
+\label{fig:ex4275}
+\end{figure*}
+
+The second shot for the comparison is 6962, which has been chosen because Thomson scattering (TS) profiles are available.
+On top of the same exercise as for 4275, we have calculated with FREEBIE equilibria with experimental TS pressure profiles.
+These equilibria of course no longer feature linear $p'$ and $FF'$ profiles.
+
 % section results (end)

### 2014-09-08 Procedure.tex
starting with 6962 results

@@
 In the optional third step, an artificial random noise is added to the calculated values of $I_\mathrm{p}$, magnetic probes and flux loops.
-In particular, for a given noise level $l$, $\tilde X = \left( {1 + U\left( { - l,l} \right)^\mathrm{T}} \right)X$, where $X$ is a row vector of the synthetic diagnostics data and $U\left( { - l,l} \right)$ is a random vector of the same shape as $X$ with a uniform distribution on $\left( { - l,l} \right)$.
+In particular, for a given noise level $\epsilon$, $\tilde X = \left( {1 + U\left( { - \epsilon, \epsilon} \right)^\mathrm{T}} \right)X$, where $X$ is a row vector of the synthetic diagnostics data and $U\left( { - \epsilon, \epsilon} \right)$ is a random vector of the same shape as $X$ with a uniform distribution on $\left( { - \epsilon, \epsilon} \right)$.
 

### 2014-09-09 Results.tex
starting with 6962 results
Example results for 6962 with noise

@@
  EFIT++ &   1.1 &          0.001 &           0.0005 &        0.005 &       0.0002 &                  0.005 &       0.004 &       0.002 &          0.04 &           0.09 &              0.03 &           0.02 &            0.05 \\
-  VacTH &  0.97 &              0 &            0.001 &       0.0006 &       0.0002 &                  0.002 &       8e-07 &       7e-05 &           nan &            nan &               nan &            nan &             nan \\
-  VacTH &  0.99 &          4e-05 &           0.0004 &        0.001 &       0.0008 &                  0.004 &       4e-07 &      0.0001 &           nan &            nan &               nan &            nan &             nan \\
-  VacTH &  1.02 &          0.002 &           0.0008 &        0.005 &        0.002 &                   0.01 &       2e-06 &       0.002 &           nan &            nan &               nan &            nan &             nan \\
-  VacTH &  1.05 &          0.006 &            0.002 &        5e-05 &        0.002 &                   0.01 &       3e-06 &        0.02 &           nan &            nan &               nan &            nan &             nan \\
-  VacTH &   1.1 &          0.005 &            0.002 &        0.002 &        0.003 &                   0.02 &       2e-06 &       0.003 &           nan &            nan &               nan &            nan &             nan \\
+  VacTH &  0.97 &              0 &            0.001 &       0.0006 &       0.0002 &                  0.002 &       8e-07 &       7e-05 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &  0.99 &          4e-05 &           0.0004 &        0.001 &       0.0008 &                  0.004 &       4e-07 &      0.0001 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &  1.02 &          0.002 &           0.0008 &        0.005 &        0.002 &                   0.01 &       2e-06 &       0.002 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &  1.05 &          0.006 &            0.002 &        5e-05 &        0.002 &                   0.01 &       3e-06 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &   1.1 &          0.005 &            0.002 &        0.002 &        0.003 &                   0.02 &       2e-06 &       0.003 &           -- &            -- &               -- &            -- &             -- \\
 \bottomrule
@@
 The second shot for the comparison is 6962, which has been chosen because Thomson scattering (TS) profiles are available.
-On top of the same exercise as for 4275, we have calculated with FREEBIE equilibria with experimental TS pressure profiles.
-These equilibria of course no longer feature linear $p'$ and $FF'$ profiles.
+In Fig.
+\ref{fig:ex6962} we show reconstructions for more realistic equilibria and an artificial noise in the synthetic diagnostic signals.
+TS pressures were used in FREEBIE equilibria, which course no longer feature linear $p'$ and $FF'$ profiles.
+It is apparent that the reconstruction is not as good as in the previous case.
+Nevertheless, the plasma shape is well reconstructed with EFIT++ and VacTH, except for the last time slice in which VacTH yields too large plasma in the upper part.
+$n_{\mathrm p} = n_{\mathrm q} = 4$ is used in this case as these values are minimum for reasonable VacTH results, while higher values are too sensitive to the input noise.
+Expectedly, EFIT++ reconstruction with magnetic data only cannot reliably reconstruct kinetic plasma parameters, such as the stored energy or $q_0$.
+Rather unexpected is a relatively good agreement of $l_\mathrm{i}$.
+However, this agreement is compensated by a large error of $\beta_{\mathrm p}$ so that the quantity $\beta_{\mathrm p} + l_{\mathrm i}/2$ remain within a 10~\% error bar.
+
+\begin{figure*}
+\centering   %\begin{center}
+\hfill{}
+\includegraphics[width=18cm]{figures/example_6962_TS_noise.pdf}
+\hfill{}
+%\end{center}
+\caption{Pressure profiles and contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 6962 with Thomson scattering pressure profiles.
+EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
+VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_{\mathrm p} = n_{\mathrm q} = 4$.}
+\label{fig:ex6962}
+\end{figure*}
+
+\begin{table*}
+\centering
+
+\begin{tabular}{lrrrrrrrrrrrrr}
+\toprule
+   % code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta \left(\beta_{\mathrm p} + l_{\mathrm i}/2 \right)$  &  $\delta q_0$ &  $\delta q_{95}$ \\
+   code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
+\midrule
+ EFIT++ &  980 &               0 &            0.005 &        0.001 &        8e-06 &                   0.01 &        0.01 &        0.01 &           0.4 &           0.03 &               0.4 &            0.2 &          0.0008 \\
+ EFIT++ & 1014 &           0.003 &            0.006 &         0.02 &         0.01 &                   0.06 &        0.03 &        0.03 &           0.3 &          0.008 &               0.3 &            0.2 &            0.08 \\
+ EFIT++ & 1080 &           0.007 &            0.002 &        0.005 &        0.002 &                   0.04 &        0.03 &        0.03 &           0.3 &           0.01 &               0.3 &            0.2 &            0.02 \\
+ EFIT++ & 1147 &           0.008 &            0.008 &         0.01 &        0.006 &                   0.06 &        0.03 &        0.02 &           0.3 &           0.06 &               0.3 &            0.3 &            0.05 \\
+ EFIT++ & 1214 &          0.0002 &            0.008 &        0.002 &        0.001 &                   0.02 &        0.02 &        0.01 &          0.04 &            0.2 &              0.06 &            0.1 &            0.01 \\
+  VacTH &  980 &               0 &             0.01 &         0.01 &        0.007 &                   0.02 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH & 1014 &           0.006 &           0.0002 &         0.01 &        0.007 &                   0.03 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH & 1080 &           0.009 &           0.0007 &        0.003 &       0.0007 &                   0.02 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH & 1147 &            0.02 &            0.007 &       0.0009 &        0.002 &                   0.01 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH & 1214 &            0.03 &            0.009 &         0.02 &         0.03 &                   0.02 &      0.0002 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
+
+ % EFIT++ & 1e+03 &               0 &            0.005 &        0.001 &        8e-06 &                   0.01 &        0.01 &        0.01 &           0.4 &           0.03 &               0.4 &            0.2 &          0.0008 \\
+ % EFIT++ & 1e+03 &           0.003 &            0.006 &         0.02 &         0.01 &                   0.06 &        0.03 &        0.03 &           0.3 &          0.008 &               0.3 &            0.2 &            0.08 \\
+ % EFIT++ & 1e+03 &           0.007 &            0.002 &        0.005 &        0.002 &                   0.04 &        0.03 &        0.03 &           0.3 &           0.01 &               0.3 &            0.2 &            0.02 \\
+ % EFIT++ & 1e+03 &           0.008 &            0.008 &         0.01 &        0.006 &                   0.06 &        0.03 &        0.02 &           0.3 &           0.06 &               0.3 &            0.3 &            0.05 \\
+ % EFIT++ & 1e+03 &          0.0002 &            0.008 &        0.002 &        0.001 &                   0.02 &        0.02 &        0.01 &          0.04 &            0.2 &              0.06 &            0.1 &            0.01 \\
+ %  VacTH & 1e+03 &               0 &             0.01 &         0.01 &        0.007 &                   0.02 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+ %  VacTH & 1e+03 &           0.006 &           0.0002 &         0.01 &        0.007 &                   0.03 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+ %  VacTH & 1e+03 &           0.009 &           0.0007 &        0.003 &       0.0007 &                   0.02 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+ %  VacTH & 1e+03 &            0.02 &            0.007 &       0.0009 &        0.002 &                   0.01 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+ %  VacTH & 1e+03 &            0.03 &            0.009 &         0.02 &         0.03 &                   0.02 &      0.0002 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
+
+\bottomrule
+\end{tabular}
+\caption{Errors for the same cases as in Fig. \ref{fig:ex6962}.}
+\label{table:ex6962}
+\end{table*}
 

### 2014-09-09 Procedure.tex
first stats figures; n_p,q renamed to n_P,Q

@@
 VacTH does not provide a full equilibrium but the plasma shape only (the target of VacTH is to provide such reconstructions in real time for a feedback control).
-Scans are performed over noise levels ($\epsilon$) and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ ($n_{p'}$, $n_{FF'}$) and the number of harmonics ($n_{\mathrm p}$, $n_{\mathrm q}$) in VacTH.
+Scans are performed over noise levels ($\epsilon$) and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ ($n_{p'}$, $n_{FF'}$) and the number of harmonics ($n_P$, $n_Q$) in VacTH.
 The following quantities are used for the comparison.

### 2014-09-09 Results.tex
first stats figures; n_p,q renamed to n_P,Q

@@
 EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
-VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_{\mathrm p} = n_{\mathrm q} = 5$.}
+VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 5$.}
 \label{fig:ex4275}
@@
 However, this agreement is compensated by a large error of $\beta_{\mathrm p}$ so that the quantity $\beta_{\mathrm p} + l_{\mathrm i}/2$ remain within a 10~\% error bar.
+Notable are large errors (up to 40~\%) in the stored energy, even for the circular plasma, which are mainly caused by incompatible pressure profiles.
 
@@
 EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
-VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_{\mathrm p} = n_{\mathrm q} = 4$.}
+VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 4$.}
 \label{fig:ex6962}
@@
 
+\begin{figure*}
+\centering   %\begin{center}
+\hfill{}
+\includegraphics[width=18cm]{figures/RZstats.pdf}
+\hfill{}
+%\end{center}
+\caption{First row: EFIT++, second row: VacTH.
+Red: linear $p'$ and $FF'$ profiles, blue: TS pressure profiles, violet: $n_{p'}=2$ or $n_{FF'}=2$, TS profiles.
+Zero noise data are scattered for a better visibility.}
+\label{fig:RZstats}
+\end{figure*}
+
+\begin{figure*}
+\centering   %\begin{center}
+\hfill{}
+\includegraphics[width=18cm]{figures/kinetic_stats.pdf}
+\hfill{}
+%\end{center}
+\caption{First row: $n_{p'}=n_{FF'}=1$, second row: either $n_{p'}=2$ or $n_{FF'}=2$.
+Red: linear $p'$ and $FF'$ profiles, blue: TS pressure profiles.
+Zero noise data are scattered for a better visibility.}
+\label{fig:kinetic_stats}
+\end{figure*}
+
 % section results (end)

### 2014-09-09 Results.tex
Statistical analysis

@@
 
-We have selected five time slices from COMPAS shots 4275 and 6962 (i.e.
-10 cases in total) for the analysis.
-These cases include circular, elongated and diverted plasmas with different currents.
+We have selected five time slices from COMPAS shots 4275 and 6962 (i.e. 10 cases in total) for the analysis. These cases include circular, elongated and diverted plasmas with different currents.
+
+\subsection{Example cases}
+
 A comparison of plasma shapes for shot 4275 is shown in Fig.
@@
 EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
-VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 5$.}
+VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 5$.
+$E_\mathrm{mp, fl}$ is the relative error of the reconstructed magnetic probes and flux loops values, respectively.}
 \label{fig:ex4275}
@@
 %\end{center}
-\caption{First row: EFIT++, second row: VacTH.
-Red: linear $p'$ and $FF'$ profiles, blue: TS pressure profiles, violet: $n_{p'}=2$ or $n_{FF'}=2$, TS profiles.
-Zero noise data are scattered for a better visibility.}
+\caption{Absolute errors in LCFS extents for convergent cases.
+EFIT++ results in the first row, VacTH in the second row.
+Selection 1 means linear $p'$ and $FF'$ in EFIT++ as well as FREEBIE, selection 2 means TS pressure profiles in FREEBIE and $n_{p'} = n_{FF'} = 1$ in EFIT++, selection 3 means TS pressure profiles in FREEBIE and $n_{p'} = 2$ in EFIT++.
+Input error is calculated as an average of $I_{\rm{p}}$, magnetic probes and flux loops values.
+Zero input error data are scattered for a better visibility.}
 \label{fig:RZstats}
@@
 Red: linear $p'$ and $FF'$ profiles, blue: TS pressure profiles.
-Zero noise data are scattered for a better visibility.}
+Zero input error data are scattered for a better visibility.}
 \label{fig:kinetic_stats}
@@
 
+\subsection{Statistical analysis} % (fold)
+\label{sub:statistical_analysis}
+
+In order to get a global overview of EFIT++ and VacTH reconstruction properties on COMPASS, we perform a scan over major code parameters and signal noise levels.
+In particular, $n_{p',FF'} = 1,2 $, $(n_\mathrm{mp}, n_\mathrm{fl}) = (16, 4), (64, 4), (8, 16)$, $\epsilon = 0, 0.02, 0.04, 0.06$, $n_{P,Q} = 4, 5, 6$.
+The same cases as above (time slices of shots 4275 and 6962) are used as target equilibria.
+For shot 6962, equilibria with TS pressure profiles and with linear $p'$ and $FF'$.
+This means there is 15 different target equilibria in total.
+
+Absolute errors of the reconstructed LCFS extents for convergent cases from the scan are shown in Fig.
+\ref{fig:RZstats}.
+We can observer that the LCFS reconstructed with EFIT++ for target linear $p'$ and $FF'$ profiles (selection 1) are within 1~cm errors.
+There are, however, cases with up to 3 cm errors in $Z_{\rm{min}}$ for the more realistic TS pressure profiles (selection 2) if $n_{p'}=1$ is used.
+This error can be reduced by using $n_{p'}=2$.
+Input errors do not pose major difficulties for EFIT++.
+
+VacTH is performing reasonably well for its most favourable diagnostic set of 8 magnetic probes and 16 flux loops and $n_P = n_Q = 4$.
+With a higher number of harmonics or with less flux loops, VacTH becomes unreliable and yields significant errors.
+Unfortunately, only 4 flux loops are currently available on COMPASS.
+In fact, it is easier for VacTH to fit magnetic probes than flux loops while magnetic probes do not fully determine the magnetic flux.
+This is also apparent in $E_\mathrm{mp}$ and $E_\mathrm{fl}$ values in Tables \ref{table:ex4275} and \ref{table:ex6962}.
+An additional optimization of the fitting weights or algorithm is probably needed.
+This can be demonstrated by an exercise reconstruction with 64 magnetic probes and 16 flux loops, whose result is significantly worse than with only 8 magnetic probes and 16 flux loops.
+
+EFIT++ internal plasma parameters reconstruction results are shown in Fig. \ref{fig:kinetic_stats}.
+
+Failure rates ...
+
+% subsection statistical_analysis (end)
+
 % section results (end)

### 2014-09-10 Results.tex
More in results

@@
 Nevertheless, the plasma shape is well reconstructed with EFIT++ and VacTH, except for the last time slice in which VacTH yields too large plasma in the upper part.
-$n_{\mathrm p} = n_{\mathrm q} = 4$ is used in this case as these values are minimum for reasonable VacTH results, while higher values are too sensitive to the input noise.
+$n_P = n_Q = 4$ is used in this case as these values are minimum for reasonable VacTH results, while higher values are too sensitive to the input noise.
 Expectedly, EFIT++ reconstruction with magnetic data only cannot reliably reconstruct kinetic plasma parameters, such as the stored energy or $q_0$.
@@
 However, this agreement is compensated by a large error of $\beta_{\mathrm p}$ so that the quantity $\beta_{\mathrm p} + l_{\mathrm i}/2$ remain within a 10~\% error bar.
-Notable are large errors (up to 40~\%) in the stored energy, even for the circular plasma, which are mainly caused by incompatible pressure profiles.
+Notable are large errors (up to 40~\%) in the stored energy, which are mainly caused by incompatible pressure profiles.
 
@@
 \hfill{}
-\includegraphics[width=18cm]{figures/kinetic_stats.pdf}
+\includegraphics[width=18cm]{figures/kinetic_stats_opt.pdf}
 \hfill{}
 %\end{center}
-\caption{First row: $n_{p'}=n_{FF'}=1$, second row: either $n_{p'}=2$ or $n_{FF'}=2$.
-Red: linear $p'$ and $FF'$ profiles, blue: TS pressure profiles.
+\caption{Internal plasma parameters relative errors for EFIT++ reconstructions using $n_{p'}=n_{FF'}=1$ in the top row and more optimized $n_{p'}$ in the bottom row.
 Zero input error data are scattered for a better visibility.}
@@
 
-EFIT++ internal plasma parameters reconstruction results are shown in Fig. \ref{fig:kinetic_stats}.
+EFIT++ internal plasma parameters reconstruction results are shown in Fig.
+\ref{fig:kinetic_stats}.
+It shows that purely magnetic reconstruction with $n_{p'}=n_{FF'}=1$ introduces (except for $I_{\rm{p}}$) a systematic error for realistic pressure profiles, i.e.
+for plasmas that do not have the same profile parametrization.
+It is known that magnetic reconstruction with EFIT is difficult for limited plasmas (without additional constraints, particularly the store energy) \cite{efit1985}.
+This suggests that using $n_{p'}=1$ for limited plasmas and $n_{p'}=2$ for diverted plasmas might lead to better results. This is demonstrated in the bottom row of Fig. \ref{fig:kinetic_stats}.
+These optimized reconstructions do not suffer from the systematic error; however, they generally increase the error bars for target equilibria with linear $p'$ and $FF'$, especially for $q_0$.
+It is also notable that $\delta l_{\rm{i}} \cong 0.1$ for all $n_{p'}=n_{FF'}=1$ reconstructions.
 
-Failure rates ...
+\begin{figure}
+\centering   %\begin{center}
+\hfill{}
+\includegraphics[width=8cm]{figures/convergence_ratio_6962.pdf}
+\hfill{}
+%\end{center}
+\caption{Ratio of converged cases to all cases, shot 6962, TS profiles. Opt refers to optimized code parameters.}
+\label{fig:convergence_ratio}
+\end{figure}
+
+Another important property is the converged cases ratio, shown in Fig.
+\ref{fig:convergence_ratio}.
+EFIT++ converges in almost all cases with any of the tested configurations and in 100~\% cases in the optimized configuration.
+$n_P = n_Q = 4$ must be used in VacTH unless the number of non-converged cases is too large.
 

### 2014-09-11 Conclusions.tex
with conclusions

%!TEX root = JUrban_SOFT2014.tex

\section{Conclusions} % (fold)
\label{sec:conclusions}

Two new codes---FREEBIE and VacTH---have been successfully set up on COMPASS, which enabled to perform an extensive cross-benchmarking and validation of free-boundary equilibrium tools. We show that FREEBIE can predict equilibria that are consistent with EFIT++ reconstructions from experimental data. FREEBIE model equilibria, either with linear $p'$ and $FF'$ profiles or with pressure profiles from Thomson scattering diagnostic, then served to assess the credibility of EFIT++ reconstructions. 
% This has not been up to now possible.

We show that magnetic reconstruction EFIT++ with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape reconstruction but introduces a systematic error in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$. The reconstruction properties can be significantly improved by using quadratic $p'$ for diverted plasmas, which removes the systematic error and also improves the LCFS reconstruction. EFIT++ converges in 100~\% cases in this regime.

Optimum parameters for VacTH have been estimated. In particular, the optimum number of harmonics is 4 otherwise VacTH fails to converge in many cases, even without any input error. 16 flux loops and only 8 magnetic must be used as VacTH input. With less flux loops or more magnetic probes the code performs significantly worse. We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape.

% section conclusions (end)

### 2014-09-11 Procedure.tex
Statistical analysis
with conclusions

@@
 In addition to the total plasma current $I_\mathrm{p}$ and the currents in individual PF circuits, 16 partial Rogowski coils and 4 flux loops are employed in this reconstruction and $p'$ and $FF'$ are assumed to be linear functions of the poloidal flux $\psi$.
+
 In the second step, FREEBIE inputs $I_\mathrm{p}$, $p'\left( {\bar \psi } \right)$ and $FF'\left( {\bar \psi } \right)$ profiles, the plasma boundary coordinates and an initial guess for the PF coils currents.
@@
 FREEBIE then seeks a solution to the Grad-Shafranov equation, including the PF coils currents, which minimizes the given plasma shape constraint.
-(This regime is called the inverse mode.) FREEBIE can naturally output arbitrary synthetic diagnostics.
+(This regime is called the inverse mode.)
+
+It should be noted here that to set up a free-boundary equilibrium code, a rather complete machine description is necessary (in particular, the PF coils geometry and circuits, limiter, vessel and other passive PF elements and magnetic diagnostics configuration).
+We adopted the description that was already available for EFIT++ and transformed it to ITM CPO's (Integrated Tokamak Modelling Consistent Physical Objects) structures, which are subsequently either used directly in FREEBIE or converted to VacTH specific input format.
+
+FREEBIE can naturally output arbitrary synthetic diagnostics.
 We use here additional 24 poloidally and 24 radially oriented partial Rogowski coils (which are actually mounted on COMPASS) and an artificial set of 16 flux loops located at the same positions as the basic magnetic probes.
@@
 $n_\mathrm{mp}=16$, $n_\mathrm{fl}=4$ refers the basic set of magnetic measurements, $n_\mathrm{mp}=64$ refers to a set of all presently mounted partial Rogowski coils on COMPASS and $n_\mathrm{fl}=16$ implies artificial flux loops positioned at the same locations as the basic magnetic probes.
+
 In the optional third step, an artificial random noise is added to the calculated values of $I_\mathrm{p}$, magnetic probes and flux loops.
@@
 The reconstructions are then compared to the original equilibrium, focusing on global parameters and geometry.
-VacTH does not provide a full equilibrium but the plasma shape only (the target of VacTH is to provide such reconstructions in real time for a feedback control).
 Scans are performed over noise levels ($\epsilon$) and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ ($n_{p'}$, $n_{FF'}$) and the number of harmonics ($n_P$, $n_Q$) in VacTH.
@@
     $Z_{\mathrm min}$, $Z_{\mathrm max}$ & minimum/maximum $Z$ coordinate of LCFS \\
+    $I_{\rm{p}}$ & plasma current \\
     $\kappa  = \frac{\left( {{Z_{{\rm{max}}}} - {Z_{{\rm{min}}}}} \right) } { \left( {{R_{{\rm{out}}}} - {R_{{\rm{in}}}}} \right) }$          & elongation   \\
@@
 
-Here, $\bar x = \int_0^V {x/V{\rm{d}}V'} $ is a volume average, $V$ is the total plasma volume, $B_{\mathrm a} = \mu _0 I_\mathrm{p} / l_{\mathrm a}$, $l_{\mathrm a}$ is the poloidal LCFS perimeter.
+Here, $\bar x = \int_0^V {x/V{\rm{d}}V'} $ is a volume average, $V$ is the total plasma volume, $B_{\mathrm a} = \mu _0 I_\mathrm{p} / l_{\mathrm a}$, $l_{\mathrm a}$ is the poloidal LCFS (last closed flux surface) perimeter.
+We also define absolute differences $\Delta x = \left| {x - {x_0}} \right|$ and relative differences $\delta x = \left| {x - {x_0}} \right|/\left| {{x_0}} \right|$, where $x$ is an arbitrary recontructed quantity and $x_0$ its target value.
+
+VacTH does not provide a full equilibrium but the plasma shape only as the target of VacTH is to provide such reconstructions in real time for a feedback control.
+The inputs (besides the machine description and code parameters) of VacTH are PF coil currents, $I_{\rm{p}}$, magnetic probes and flux loops measurements and the initial axis and X-point coordinates (the coordinates can be fixed as code parameters).
 

### 2014-09-11 Results.tex
with conclusions

@@
 An additional optimization of the fitting weights or algorithm is probably needed.
-This can be demonstrated by an exercise reconstruction with 64 magnetic probes and 16 flux loops, whose result is significantly worse than with only 8 magnetic probes and 16 flux loops.
+The current behaviour might be quite anti-intuitive as VacTH performs significantly worse with 16 flux loops and 16 or 64 magnetic probes in comparison to 16 flux loops and only 8 magnetic probes.
 

### 2014-09-11 Abstract.tex
FED master tex document
Simplified abstract, DRAFT watermark, github link

@@
-\section{Abstract}
+%!TEX root = JUrban_SOFT2014.tex
 
-Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developed or considerably updated, are used on the medium-size COMPASS tokamak [R.
-Pánek et al., Czech J Phys 56, B125, 2006].
+\begin{abstract}
+
+Various MHD (magnetohydrodynamic) equilibrium tools, some of which being recently developed or considerably updated, are used on the COMPASS tokamak at IPP Prague.
 MHD equilibrium is a fundamental property of the tokamak plasma, whose knowledge is required for many diagnostics and modelling tools.
@@
 We present here benchmarks and comparisons to experimental data of the EFIT++ reconstruction code [L.C.
-Appel et al., to be submitted to Nucl.
-Fusion], the free-boundary equilibrium code FREEBIE  [J.-F.
+Appel et al., EPS 2006, P2.184], the free-boundary equilibrium code FREEBIE  [J.-F.
 Artaud, S.H.
@@
 Faugeras et al., PPCF 2014, accepted].
-We demonstrate that FREEBIE can calculate the equilibrium and corresponding poloidal field (PF) coils currents for given plasma parameters.
-Both EFIT++ and VacTH can reconstruct equilibria generated by FREEBIE from synthetic diagnostic data (including an artificial noise) and hence might be suitable for real-time control.
-Optimum reconstruction parameters are estimated; in addition, possible enhancements using more diagnostics are discussed and simulated using synthetic diagnostics.
-FREEBIE can also calculate the temporal evolution of the poloidal field coils currents for a whole plasma scenario.
+We demonstrate that FREEBIE can calculate the equilibrium and corresponding poloidal field (PF) coils currents consistently with EFIT++ reconstructions from experimental data.
+Both EFIT++ and VacTH can reconstruct equilibria generated by FREEBIE from synthetic, optionally noisy diagnostic data.
+Hence, VacTH is suitable for real-time control.
+Optimum reconstruction parameters are estimated.
+
+\end{abstract}

### 2014-09-18 Procedure.tex
mainly updated figures, including some data

@@
 Here, $\bar x = \int_0^V {x/V{\rm{d}}V'} $ is a volume average, $V$ is the total plasma volume, $B_{\mathrm a} = \mu _0 I_\mathrm{p} / l_{\mathrm a}$, $l_{\mathrm a}$ is the poloidal LCFS (last closed flux surface) perimeter.
-We also define absolute differences $\Delta x = \left| {x - {x_0}} \right|$ and relative differences $\delta x = \left| {x - {x_0}} \right|/\left| {{x_0}} \right|$, where $x$ is an arbitrary recontructed quantity and $x_0$ its target value.
+We also define absolute differences $\Delta x = {{x_0} - x} $ and relative differences $\delta x = \left| {{x_0} - x} \right|/\left| {{x_0}} \right|$, where $x$ is an arbitrary recontructed quantity and $x_0$ its target value.
 

### 2014-09-18 Results.tex
mainly updated figures, including some data

@@
 \centering
-
+\small
 \begin{tabular}{lrrrrrrrrrrrrr}
 \toprule
-   code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
+   code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
 \midrule
@@
 %\end{center}
-\caption{Pressure profiles and contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 6962 with Thomson scattering pressure profiles.
-EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
+\caption{Pressure profiles and contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data with 3~\% random noise, shot 6962 with Thomson scattering pressure profiles.
+EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{FF'} = 1$.
 VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 4$.}
@@
 \centering
-
+\small
 \begin{tabular}{lrrrrrrrrrrrrr}
@@
    % code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta \left(\beta_{\mathrm p} + l_{\mathrm i}/2 \right)$  &  $\delta q_0$ &  $\delta q_{95}$ \\
-   code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
+   code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
 \midrule
- EFIT++ &  980 &               0 &            0.005 &        0.001 &        8e-06 &                   0.01 &        0.01 &        0.01 &           0.4 &           0.03 &               0.4 &            0.2 &          0.0008 \\
- EFIT++ & 1014 &           0.003 &            0.006 &         0.02 &         0.01 &                   0.06 &        0.03 &        0.03 &           0.3 &          0.008 &               0.3 &            0.2 &            0.08 \\
- EFIT++ & 1080 &           0.007 &            0.002 &        0.005 &        0.002 &                   0.04 &        0.03 &        0.03 &           0.3 &           0.01 &               0.3 &            0.2 &            0.02 \\
- EFIT++ & 1147 &           0.008 &            0.008 &         0.01 &        0.006 &                   0.06 &        0.03 &        0.02 &           0.3 &           0.06 &               0.3 &            0.3 &            0.05 \\
- EFIT++ & 1214 &          0.0002 &            0.008 &        0.002 &        0.001 &                   0.02 &        0.02 &        0.01 &          0.04 &            0.2 &              0.06 &            0.1 &            0.01 \\
-  VacTH &  980 &               0 &             0.01 &         0.01 &        0.007 &                   0.02 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH & 1014 &           0.006 &           0.0002 &         0.01 &        0.007 &                   0.03 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH & 1080 &           0.009 &           0.0007 &        0.003 &       0.0007 &                   0.02 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH & 1147 &            0.02 &            0.007 &       0.0009 &        0.002 &                   0.01 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH & 1214 &            0.03 &            0.009 &         0.02 &         0.03 &                   0.02 &      0.0002 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
-
- % EFIT++ & 1e+03 &               0 &            0.005 &        0.001 &        8e-06 &                   0.01 &        0.01 &        0.01 &           0.4 &           0.03 &               0.4 &            0.2 &          0.0008 \\
- % EFIT++ & 1e+03 &           0.003 &            0.006 &         0.02 &         0.01 &                   0.06 &        0.03 &        0.03 &           0.3 &          0.008 &               0.3 &            0.2 &            0.08 \\
- % EFIT++ & 1e+03 &           0.007 &            0.002 &        0.005 &        0.002 &                   0.04 &        0.03 &        0.03 &           0.3 &           0.01 &               0.3 &            0.2 &            0.02 \\
- % EFIT++ & 1e+03 &           0.008 &            0.008 &         0.01 &        0.006 &                   0.06 &        0.03 &        0.02 &           0.3 &           0.06 &               0.3 &            0.3 &            0.05 \\
- % EFIT++ & 1e+03 &          0.0002 &            0.008 &        0.002 &        0.001 &                   0.02 &        0.02 &        0.01 &          0.04 &            0.2 &              0.06 &            0.1 &            0.01 \\
- %  VacTH & 1e+03 &               0 &             0.01 &         0.01 &        0.007 &                   0.02 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
- %  VacTH & 1e+03 &           0.006 &           0.0002 &         0.01 &        0.007 &                   0.03 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
- %  VacTH & 1e+03 &           0.009 &           0.0007 &        0.003 &       0.0007 &                   0.02 &       3e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
- %  VacTH & 1e+03 &            0.02 &            0.007 &       0.0009 &        0.002 &                   0.01 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
- %  VacTH & 1e+03 &            0.03 &            0.009 &         0.02 &         0.03 &                   0.02 &      0.0002 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
-
+ EFIT++ &    980 &               0 &            0.009 &       -0.003 &        0.003 &                   0.01 &        0.04 &        0.01 &           0.1 &            0.3 &               0.1 &            0.5 &            0.02 \\
+ EFIT++ &   1014 &          0.0004 &          -0.0005 &       -0.001 &        0.001 &                  0.002 &        0.01 &        0.01 &         0.006 &            0.1 &             0.003 &           0.07 &           0.003 \\
+ EFIT++ &   1080 &          -0.002 &           -0.002 &       -0.002 &        0.002 &                  0.003 &        0.01 &        0.02 &           0.2 &            0.1 &               0.2 &           0.06 &            0.02 \\
+ EFIT++ &   1147 &          -0.002 &          -0.0006 &       -0.007 &       -0.002 &                  0.006 &        0.01 &        0.02 &           0.1 &            0.2 &               0.1 &            0.2 &            0.01 \\
+ EFIT++ &   1214 &          -0.004 &            0.007 &        0.006 &       -0.004 &                   0.04 &        0.03 &        0.01 &           0.2 &            0.3 &               0.2 &           0.03 &           0.001 \\
+  VacTH &    980 &               0 &            -0.01 &         0.01 &        -0.02 &                   0.04 &      0.0002 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &   1014 &           0.006 &           -0.003 &        -0.01 &       -0.001 &                   0.02 &       7e-05 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &   1080 &            0.01 &           -0.003 &        0.004 &       -0.003 &                   0.01 &       3e-05 &       0.009 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &   1147 &            0.02 &           -0.003 &       -0.002 &        0.002 &                   0.04 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+  VacTH &   1214 &            0.01 &            0.001 &        -0.02 &         0.02 &                   0.07 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
 \bottomrule
@@
 EFIT++ results in the first row, VacTH in the second row.
-Selection 1 means linear $p'$ and $FF'$ in EFIT++ as well as FREEBIE, selection 2 means TS pressure profiles in FREEBIE and $n_{p'} = n_{FF'} = 1$ in EFIT++, selection 3 means TS pressure profiles in FREEBIE and $n_{p'} = 2$ in EFIT++.
+S1 denotes linear $p'$ and $FF'$ in EFIT++ as well as FREEBIE, s2 denotes TS pressure profiles in FREEBIE and $n_{p'} = n_{FF'} = 1$ in EFIT++, s3 denotes TS pressure profiles in FREEBIE and $n_{p'} = 2$ in EFIT++.
+Full lines show the means.
+VacTH parameters are $n_P=n_Q=4$, ``8 mp, 16 fl'' denotes $n_\mathrm{mp}=8$, $n_\mathrm{fl}=16$.
 Input error is calculated as an average of $I_{\rm{p}}$, magnetic probes and flux loops values.
@@
 This suggests that using $n_{p'}=1$ for limited plasmas and $n_{p'}=2$ for diverted plasmas might lead to better results. This is demonstrated in the bottom row of Fig. \ref{fig:kinetic_stats}.
-These optimized reconstructions do not suffer from the systematic error; however, they generally increase the error bars for target equilibria with linear $p'$ and $FF'$, especially for $q_0$.
+Reconstructions with such optimized parameters do not suffer from the systematic error; however, they generally increase the error bars for target equilibria with linear $p'$ and $FF'$, especially for $q_0$.
 It is also notable that $\delta l_{\rm{i}} \cong 0.1$ for all $n_{p'}=n_{FF'}=1$ reconstructions.
@@
 \ref{fig:convergence_ratio}.
-EFIT++ converges in almost all cases with any of the tested configurations and in 100~\% cases in the optimized configuration.
+EFIT++ converges in almost all cases with any of the tested configurations and in 100~\% cases in the optimized configuration (i.e.
+with $n_{p'}=2$ for diverted plasmas).
 $n_P = n_Q = 4$ must be used in VacTH unless the number of non-converged cases is too large.
+Quite interestingly, optimized VacTH convergence rate drops significantly around 2~\% input noise.
 

### 2014-09-22 Results.tex
(minor) corrections from Ivan

@@
 for plasmas that do not have the same profile parametrization.
-It is known that magnetic reconstruction with EFIT is difficult for limited plasmas (without additional constraints, particularly the store energy) \cite{efit1985}.
+It is known that magnetic reconstruction with EFIT is difficult for limiter plasmas (without additional constraints, particularly the stored energy) \cite{efit1985}.
 This suggests that using $n_{p'}=1$ for limited plasmas and $n_{p'}=2$ for diverted plasmas might lead to better results. This is demonstrated in the bottom row of Fig. \ref{fig:kinetic_stats}.

### 2014-09-29 Conclusions.tex
minor rephrase of conclusions

@@
 
-We show that magnetic reconstruction EFIT++ with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape reconstruction but introduces a systematic error in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$.
-The reconstruction properties can be significantly improved by using quadratic $p'$ for diverted plasmas, which removes the systematic error and also improves the LCFS reconstruction.
+We show that magnetic reconstruction EFIT++ with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape reconstruction but introduces systematic errors both in the shape and in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$.
+The reconstruction properties can be significantly improved by using quadratic $p'$ for divertor plasmas, which removes the systematic error and also improves the LCFS reconstruction.
 EFIT++ converges in 100~\% cases in this regime.

### 2014-10-04 Conclusions.tex
* shortening to 4 pages * changed optimized EFIT parameters to quadratic p' for diverted AND ELONGATED plasma * created B&W figure versions

@@
 We show that magnetic reconstruction EFIT++ with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape reconstruction but introduces systematic errors both in the shape and in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$.
-The reconstruction properties can be significantly improved by using quadratic $p'$ for divertor plasmas, which removes the systematic error and also improves the LCFS reconstruction.
+The reconstruction properties can be significantly improved by using quadratic $p'$ for elongated and divertor plasmas, which removes the systematic error and also improves the LCFS reconstruction.
 EFIT++ converges in 100~\% cases in this regime.

### 2014-10-04 Results.tex
* shortening to 4 pages * changed optimized EFIT parameters to quadratic p' for diverted AND ELONGATED plasma * created B&W figure versions

--- 2014-09-18 Results.tex
@@
 
+\begin{figure*}[!htb]
+\centering   %\begin{center}
+\hfill{}
+\includegraphics[width=18cm]{figures/example_6962.pdf}
+\hfill{}
+%\end{center}
+\caption{EFIT++ reconstructed pressure profiles and contours of $\bar\psi=\left(0.5,1\right)$ and VacTH LCFS from FREEBIE data, shot 6962 with Thomson scattering pressure profiles.
+EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{FF'} = 1$.
+VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 4$.
+3~\% random input data noise is used in the case of VacTH and EFIT++ with $n_{p'} = 2$, zero noise otherwise.}
+\label{fig:ex6962}
+\end{figure*}
+
 We have selected five time slices from COMPAS shots 4275 and 6962 (i.e. 10 cases in total) for the analysis. These cases include circular, elongated and diverted plasmas with different currents.
@@
 
-A comparison of plasma shapes for shot 4275 is shown in Fig.
+Examples of EFIT++ and VacTH reconstructions are shown in Fig.
+\ref{fig:ex6962}.
+The results are quite typical.
+EFIT++ with a linear $p'$ yields an enhanced LCFS error, in particular in the first, elliptical plasma case, even with zero input data noise.
+On the other hand, quadratic $p'$ reconstructs the plasma shape correctly even with a noisy input.
+A similar observation applies to the pressure profiles, except that for the elliptical case, the pressure is not well reconstructed for either $n_{p'}$.
+
+VacTH reconstructs the LCFS reasonably, even with noisy inputs.
+Although a bending artefact emerge on the inboard side.
+Similar artefacts can be observed in other VacTH results as well.
+This is probably a result of the specific COMPASS configuration as such a behaviour was not observed in the case of WEST \cite{vacthref}.
+$n_P = n_Q = 4$ is used in this case as these values are minimum for reasonable VacTH results, while higher values are too sensitive to the input noise.
+
+% A comparison of plasma shapes for shot 4275 is shown in Fig.
 \ref{fig:ex4275}.
@@
 
-\begin{table*}
-\centering
-\small
-\begin{tabular}{lrrrrrrrrrrrrr}
-\toprule
-   code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
-\midrule
- EFIT++ &  0.97 &              0 &            0.002 &        0.001 &        0.001 &                  0.003 &       0.001 &      0.0009 &          0.04 &           0.09 &              0.03 &           0.03 &           0.007 \\
- EFIT++ &  0.99 &          4e-05 &            9e-05 &        0.001 &        0.001 &                  0.004 &       0.001 &      0.0006 &          0.04 &           0.09 &              0.04 &           0.02 &           0.005 \\
- EFIT++ &  1.02 &         0.0005 &           0.0002 &        0.002 &        0.002 &                  0.008 &       0.002 &       0.002 &          0.02 &            0.1 &              0.02 &           0.02 &           0.009 \\
- EFIT++ &  1.05 &          0.001 &           0.0008 &        4e-05 &       0.0003 &                  0.004 &       0.003 &       0.005 &          0.01 &           0.07 &              0.02 &           0.01 &           0.009 \\
- EFIT++ &   1.1 &          0.001 &           0.0005 &        0.005 &       0.0002 &                  0.005 &       0.004 &       0.002 &          0.04 &           0.09 &              0.03 &           0.02 &            0.05 \\
-  VacTH &  0.97 &              0 &            0.001 &       0.0006 &       0.0002 &                  0.002 &       8e-07 &       7e-05 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &  0.99 &          4e-05 &           0.0004 &        0.001 &       0.0008 &                  0.004 &       4e-07 &      0.0001 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &  1.02 &          0.002 &           0.0008 &        0.005 &        0.002 &                   0.01 &       2e-06 &       0.002 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &  1.05 &          0.006 &            0.002 &        5e-05 &        0.002 &                   0.01 &       3e-06 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &   1.1 &          0.005 &            0.002 &        0.002 &        0.003 &                   0.02 &       2e-06 &       0.003 &           -- &            -- &               -- &            -- &             -- \\
-\bottomrule
-\end{tabular}
+% \begin{table*}
+% \centering
+% \small
+% \begin{tabular}{lrrrrrrrrrrrrr}
+% \toprule
+%    code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
+% \midrule
+%  EFIT++ &  0.97 &              0 &            0.002 &        0.001 &        0.001 &                  0.003 &       0.001 &      0.0009 &          0.04 &           0.09 &              0.03 &           0.03 &           0.007 \\
+%  EFIT++ &  0.99 &          4e-05 &            9e-05 &        0.001 &        0.001 &                  0.004 &       0.001 &      0.0006 &          0.04 &           0.09 &              0.04 &           0.02 &           0.005 \\
+%  EFIT++ &  1.02 &         0.0005 &           0.0002 &        0.002 &        0.002 &                  0.008 &       0.002 &       0.002 &          0.02 &            0.1 &              0.02 &           0.02 &           0.009 \\
+%  EFIT++ &  1.05 &          0.001 &           0.0008 &        4e-05 &       0.0003 &                  0.004 &       0.003 &       0.005 &          0.01 &           0.07 &              0.02 &           0.01 &           0.009 \\
+%  EFIT++ &   1.1 &          0.001 &           0.0005 &        0.005 &       0.0002 &                  0.005 &       0.004 &       0.002 &          0.04 &           0.09 &              0.03 &           0.02 &            0.05 \\
+%   VacTH &  0.97 &              0 &            0.001 &       0.0006 &       0.0002 &                  0.002 &       8e-07 &       7e-05 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &  0.99 &          4e-05 &           0.0004 &        0.001 &       0.0008 &                  0.004 &       4e-07 &      0.0001 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &  1.02 &          0.002 &           0.0008 &        0.005 &        0.002 &                   0.01 &       2e-06 &       0.002 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &  1.05 &          0.006 &            0.002 &        5e-05 &        0.002 &                   0.01 &       3e-06 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &   1.1 &          0.005 &            0.002 &        0.002 &        0.003 &                   0.02 &       2e-06 &       0.003 &           -- &            -- &               -- &            -- &             -- \\
+% \bottomrule
+% \end{tabular}
 
-\caption{Errors for the same cases as in Fig. \ref{fig:ex4275}.}
-\label{table:ex4275}
-\end{table*}
+% \caption{Errors for the same cases as in Fig. \ref{fig:ex4275}.}
+% \label{table:ex4275}
+% \end{table*}
 
-\begin{figure*}
-\centering   %\begin{center}
-\hfill{}
-\includegraphics[width=18cm]{figures/example_4275.pdf}
-\hfill{}
-%\end{center}
-\caption{Contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 4275.
+% \begin{figure*}
+% \centering   %\begin{center}
+% \hfill{}
+% \includegraphics[width=18cm]{figures/example_4275.pdf}
+% \hfill{}
+% %\end{center}
+% \caption{Contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 4275.
 EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
@@
 $E_\mathrm{mp, fl}$ is the relative error of the reconstructed magnetic probes and flux loops values, respectively.}
-\label{fig:ex4275}
-\end{figure*}
+% \label{fig:ex4275}
+% \end{figure*}
 
-The second shot for the comparison is 6962, which has been chosen because Thomson scattering (TS) profiles are available.
+% The second shot for the comparison is 6962, which has been chosen because Thomson scattering (TS) profiles are available.
 In Fig.
@@
 TS pressures were used in FREEBIE equilibria, which course no longer feature linear $p'$ and $FF'$ profiles.
-It is apparent that the reconstruction is not as good as in the previous case.
+% It is apparent that the reconstruction is not as good as in the previous case.
 Nevertheless, the plasma shape is well reconstructed with EFIT++ and VacTH, except for the last time slice in which VacTH yields too large plasma in the upper part.
-$n_P = n_Q = 4$ is used in this case as these values are minimum for reasonable VacTH results, while higher values are too sensitive to the input noise.
-Expectedly, EFIT++ reconstruction with magnetic data only cannot reliably reconstruct kinetic plasma parameters, such as the stored energy or $q_0$.
+
+% Expectedly, EFIT++ reconstruction with magnetic data only cannot reliably reconstruct kinetic plasma parameters, such as the stored energy or $q_0$.
 Rather unexpected is a relatively good agreement of $l_\mathrm{i}$.
@@
 
-\begin{figure*}
-\centering   %\begin{center}
-\hfill{}
-\includegraphics[width=18cm]{figures/example_6962_TS_noise.pdf}
-\hfill{}
-%\end{center}
-\caption{Pressure profiles and contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data with 3~\% random noise, shot 6962 with Thomson scattering pressure profiles.
-EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{FF'} = 1$.
-VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 4$.}
-\label{fig:ex6962}
-\end{figure*}
+% \begin{table*}
+% \centering
+% \small
+% \begin{tabular}{lrrrrrrrrrrrrr}
+% \toprule
+%    % code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta \left(\beta_{\mathrm p} + l_{\mathrm i}/2 \right)$  &  $\delta q_0$ &  $\delta q_{95}$ \\
+%    code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
+% \midrule
+%  EFIT++ &    980 &               0 &            0.009 &       -0.003 &        0.003 &                   0.01 &        0.04 &        0.01 &           0.1 &            0.3 &               0.1 &            0.5 &            0.02 \\
+%  EFIT++ &   1014 &          0.0004 &          -0.0005 &       -0.001 &        0.001 &                  0.002 &        0.01 &        0.01 &         0.006 &            0.1 &             0.003 &           0.07 &           0.003 \\
+%  EFIT++ &   1080 &          -0.002 &           -0.002 &       -0.002 &        0.002 &                  0.003 &        0.01 &        0.02 &           0.2 &            0.1 &               0.2 &           0.06 &            0.02 \\
+%  EFIT++ &   1147 &          -0.002 &          -0.0006 &       -0.007 &       -0.002 &                  0.006 &        0.01 &        0.02 &           0.1 &            0.2 &               0.1 &            0.2 &            0.01 \\
+%  EFIT++ &   1214 &          -0.004 &            0.007 &        0.006 &       -0.004 &                   0.04 &        0.03 &        0.01 &           0.2 &            0.3 &               0.2 &           0.03 &           0.001 \\
+%   VacTH &    980 &               0 &            -0.01 &         0.01 &        -0.02 &                   0.04 &      0.0002 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &   1014 &           0.006 &           -0.003 &        -0.01 &       -0.001 &                   0.02 &       7e-05 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &   1080 &            0.01 &           -0.003 &        0.004 &       -0.003 &                   0.01 &       3e-05 &       0.009 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &   1147 &            0.02 &           -0.003 &       -0.002 &        0.002 &                   0.04 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+%   VacTH &   1214 &            0.01 &            0.001 &        -0.02 &         0.02 &                   0.07 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
+% \bottomrule
+% \end{tabular}
+% \caption{Errors for the same cases as in Fig. \ref{fig:ex6962}.}
+% \label{table:ex6962}
+% \end{table*}
 
-\begin{table*}
-\centering
-\small
-\begin{tabular}{lrrrrrrrrrrrrr}
-\toprule
-   % code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta \left(\beta_{\mathrm p} + l_{\mathrm i}/2 \right)$  &  $\delta q_0$ &  $\delta q_{95}$ \\
-   code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
-\midrule
- EFIT++ &    980 &               0 &            0.009 &       -0.003 &        0.003 &                   0.01 &        0.04 &        0.01 &           0.1 &            0.3 &               0.1 &            0.5 &            0.02 \\
- EFIT++ &   1014 &          0.0004 &          -0.0005 &       -0.001 &        0.001 &                  0.002 &        0.01 &        0.01 &         0.006 &            0.1 &             0.003 &           0.07 &           0.003 \\
- EFIT++ &   1080 &          -0.002 &           -0.002 &       -0.002 &        0.002 &                  0.003 &        0.01 &        0.02 &           0.2 &            0.1 &               0.2 &           0.06 &            0.02 \\
- EFIT++ &   1147 &          -0.002 &          -0.0006 &       -0.007 &       -0.002 &                  0.006 &        0.01 &        0.02 &           0.1 &            0.2 &               0.1 &            0.2 &            0.01 \\
- EFIT++ &   1214 &          -0.004 &            0.007 &        0.006 &       -0.004 &                   0.04 &        0.03 &        0.01 &           0.2 &            0.3 &               0.2 &           0.03 &           0.001 \\
-  VacTH &    980 &               0 &            -0.01 &         0.01 &        -0.02 &                   0.04 &      0.0002 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &   1014 &           0.006 &           -0.003 &        -0.01 &       -0.001 &                   0.02 &       7e-05 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &   1080 &            0.01 &           -0.003 &        0.004 &       -0.003 &                   0.01 &       3e-05 &       0.009 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &   1147 &            0.02 &           -0.003 &       -0.002 &        0.002 &                   0.04 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-  VacTH &   1214 &            0.01 &            0.001 &        -0.02 &         0.02 &                   0.07 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-\bottomrule
-\end{tabular}
-\caption{Errors for the same cases as in Fig. \ref{fig:ex6962}.}
-\label{table:ex6962}
-\end{table*}
-
-\begin{figure*}
+\begin{figure*}[!htb]
 \centering   %\begin{center}
@@
 
-\begin{figure*}
+\begin{figure*}[!htb]
 \centering   %\begin{center}
@@
 Unfortunately, only 4 flux loops are currently available on COMPASS.
-In fact, it is easier for VacTH to fit magnetic probes than flux loops while magnetic probes do not fully determine the magnetic flux.
-This is also apparent in $E_\mathrm{mp}$ and $E_\mathrm{fl}$ values in Tables \ref{table:ex4275} and \ref{table:ex6962}.
+In fact, it is easier for VacTH to fit magnetic probes than flux loops
+% while magnetic probes do not fully determine the magnetic flux. 
+% This is also apparent in $E_\mathrm{mp}$ and $E_\mathrm{fl}$ values in Tables \ref{table:ex4275} and \ref{table:ex6962}. 
 An additional optimization of the fitting weights or algorithm is probably needed.
@@
 for plasmas that do not have the same profile parametrization.
-It is known that magnetic reconstruction with EFIT is difficult for limited plasmas (without additional constraints, particularly the store energy) \cite{efit1985}.
-This suggests that using $n_{p'}=1$ for limited plasmas and $n_{p'}=2$ for diverted plasmas might lead to better results. This is demonstrated in the bottom row of Fig. \ref{fig:kinetic_stats}.
+It is known that magnetic reconstruction with EFIT is difficult for small circular plasmas (without additional constraints, particularly the stored energy) \cite{efit1985}.
+This suggests that using $n_{p'}=1$ for circular plasmas and $n_{p'}=2$ for elongated and diverted plasmas might lead to better results.
+This is demonstrated in the bottom row of Fig.
+\ref{fig:kinetic_stats}.
 Reconstructions with such optimized parameters do not suffer from the systematic error; however, they generally increase the error bars for target equilibria with linear $p'$ and $FF'$, especially for $q_0$.

### 2014-10-04 Results.tex
submitted version: * no subdirectories * removed comments * added cover letter and research highlights

@@
 \hfill{}
-\includegraphics[width=18cm]{figures/example_6962.pdf}
+\includegraphics[width=18cm]{example_6962.pdf}
 \hfill{}
@@
 
-% A comparison of plasma shapes for shot 4275 is shown in Fig.
-\ref{fig:ex4275}.
-Numerical values of reconstruction errors are presented in Table \ref{table:ex4275}.
-We can observe a very good agreement between the original equilibrium and the reconstructed shapes.
-In this case, FREEBIE was using linear $p'$ and $FF'$ polynomials so that the EFIT++ model agrees with the target data.
-VacTH uses 8 magnetic probes and 16 flux loops.
-As we discuss later, flux loops are essential for reliable VacTH results.
-Even global kinetic properties are well reconstructed in EFIT++; the largest error around 10~\% is in $l_{\mathrm i}$ (i.e.
-basically in the toroidal current density profile).
-
-% \begin{table*}
-% \centering
-% \small
-% \begin{tabular}{lrrrrrrrrrrrrr}
-% \toprule
-%    code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
-% \midrule
-%  EFIT++ &  0.97 &              0 &            0.002 &        0.001 &        0.001 &                  0.003 &       0.001 &      0.0009 &          0.04 &           0.09 &              0.03 &           0.03 &           0.007 \\
-%  EFIT++ &  0.99 &          4e-05 &            9e-05 &        0.001 &        0.001 &                  0.004 &       0.001 &      0.0006 &          0.04 &           0.09 &              0.04 &           0.02 &           0.005 \\
-%  EFIT++ &  1.02 &         0.0005 &           0.0002 &        0.002 &        0.002 &                  0.008 &       0.002 &       0.002 &          0.02 &            0.1 &              0.02 &           0.02 &           0.009 \\
-%  EFIT++ &  1.05 &          0.001 &           0.0008 &        4e-05 &       0.0003 &                  0.004 &       0.003 &       0.005 &          0.01 &           0.07 &              0.02 &           0.01 &           0.009 \\
-%  EFIT++ &   1.1 &          0.001 &           0.0005 &        0.005 &       0.0002 &                  0.005 &       0.004 &       0.002 &          0.04 &           0.09 &              0.03 &           0.02 &            0.05 \\
-%   VacTH &  0.97 &              0 &            0.001 &       0.0006 &       0.0002 &                  0.002 &       8e-07 &       7e-05 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &  0.99 &          4e-05 &           0.0004 &        0.001 &       0.0008 &                  0.004 &       4e-07 &      0.0001 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &  1.02 &          0.002 &           0.0008 &        0.005 &        0.002 &                   0.01 &       2e-06 &       0.002 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &  1.05 &          0.006 &            0.002 &        5e-05 &        0.002 &                   0.01 &       3e-06 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &   1.1 &          0.005 &            0.002 &        0.002 &        0.003 &                   0.02 &       2e-06 &       0.003 &           -- &            -- &               -- &            -- &             -- \\
-% \bottomrule
-% \end{tabular}
-
-% \caption{Errors for the same cases as in Fig. \ref{fig:ex4275}.}
-% \label{table:ex4275}
-% \end{table*}
-
-% \begin{figure*}
-% \centering   %\begin{center}
-% \hfill{}
-% \includegraphics[width=18cm]{figures/example_4275.pdf}
-% \hfill{}
-% %\end{center}
-% \caption{Contours of $\bar\psi=\left(0.25,0.5,0.75,1\right)$, reconstruction from FREEBIE data, shot 4275.
-EFIT++ parameters: $n_\mathrm{mp} = 16$, $n_\mathrm{fl} = 4$, $n_{p'} = n_{FF'} = 1$.
-VacTH parameters: $n_\mathrm{mp} = 8$, $n_\mathrm{fl} = 16$, $n_P = n_Q = 5$.
-$E_\mathrm{mp, fl}$ is the relative error of the reconstructed magnetic probes and flux loops values, respectively.}
-% \label{fig:ex4275}
-% \end{figure*}
-
-% The second shot for the comparison is 6962, which has been chosen because Thomson scattering (TS) profiles are available.
-In Fig.
-\ref{fig:ex6962} we show reconstructions for more realistic equilibria and an artificial noise in the synthetic diagnostic signals.
-TS pressures were used in FREEBIE equilibria, which course no longer feature linear $p'$ and $FF'$ profiles.
-% It is apparent that the reconstruction is not as good as in the previous case.
-Nevertheless, the plasma shape is well reconstructed with EFIT++ and VacTH, except for the last time slice in which VacTH yields too large plasma in the upper part.
-
-% Expectedly, EFIT++ reconstruction with magnetic data only cannot reliably reconstruct kinetic plasma parameters, such as the stored energy or $q_0$.
-Rather unexpected is a relatively good agreement of $l_\mathrm{i}$.
-However, this agreement is compensated by a large error of $\beta_{\mathrm p}$ so that the quantity $\beta_{\mathrm p} + l_{\mathrm i}/2$ remain within a 10~\% error bar.
-Notable are large errors (up to 40~\%) in the stored energy, which are mainly caused by incompatible pressure profiles.
-
-% \begin{table*}
-% \centering
-% \small
-% \begin{tabular}{lrrrrrrrrrrrrr}
-% \toprule
-%    % code &  time &  $\Delta R_{\mathrm in}$ &  $\Delta R_{\mathrm out}$ &  $\Delta Z_{\mathrm min}$ &  $\Delta Z_{\mathrm max}$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta \left(\beta_{\mathrm p} + l_{\mathrm i}/2 \right)$  &  $\delta q_0$ &  $\delta q_{95}$ \\
-%    code &  time &  $\left| \Delta R_{\mathrm in} \right|$ &  $\left| \Delta R_{\mathrm out} \right|$ &  $\left| \Delta Z_{\mathrm min} \right|$ &  $\left| \Delta Z_{\mathrm max} \right|$ &  $\delta \kappa$ &  $E_\mathrm{mp}$ &  $E_\mathrm{fl}$ &  $\delta W$ &  $\delta l_{\mathrm i}$ &  $\delta \beta_{\mathrm p}$ &  $\delta q_0$ &  $\delta q_{95}$ \\
-% \midrule
-%  EFIT++ &    980 &               0 &            0.009 &       -0.003 &        0.003 &                   0.01 &        0.04 &        0.01 &           0.1 &            0.3 &               0.1 &            0.5 &            0.02 \\
-%  EFIT++ &   1014 &          0.0004 &          -0.0005 &       -0.001 &        0.001 &                  0.002 &        0.01 &        0.01 &         0.006 &            0.1 &             0.003 &           0.07 &           0.003 \\
-%  EFIT++ &   1080 &          -0.002 &           -0.002 &       -0.002 &        0.002 &                  0.003 &        0.01 &        0.02 &           0.2 &            0.1 &               0.2 &           0.06 &            0.02 \\
-%  EFIT++ &   1147 &          -0.002 &          -0.0006 &       -0.007 &       -0.002 &                  0.006 &        0.01 &        0.02 &           0.1 &            0.2 &               0.1 &            0.2 &            0.01 \\
-%  EFIT++ &   1214 &          -0.004 &            0.007 &        0.006 &       -0.004 &                   0.04 &        0.03 &        0.01 &           0.2 &            0.3 &               0.2 &           0.03 &           0.001 \\
-%   VacTH &    980 &               0 &            -0.01 &         0.01 &        -0.02 &                   0.04 &      0.0002 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &   1014 &           0.006 &           -0.003 &        -0.01 &       -0.001 &                   0.02 &       7e-05 &        0.02 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &   1080 &            0.01 &           -0.003 &        0.004 &       -0.003 &                   0.01 &       3e-05 &       0.009 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &   1147 &            0.02 &           -0.003 &       -0.002 &        0.002 &                   0.04 &       5e-05 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-%   VacTH &   1214 &            0.01 &            0.001 &        -0.02 &         0.02 &                   0.07 &      0.0001 &        0.01 &           -- &            -- &               -- &            -- &             -- \\
-% \bottomrule
-% \end{tabular}
-% \caption{Errors for the same cases as in Fig. \ref{fig:ex6962}.}
-% \label{table:ex6962}
-% \end{table*}
-
 \begin{figure*}[!htb]
@@
 \hfill{}
-\includegraphics[width=18cm]{figures/RZstats.pdf}
+\includegraphics[width=18cm]{RZstats.pdf}
 \hfill{}
@@
 \hfill{}
-\includegraphics[width=18cm]{figures/kinetic_stats_opt.pdf}
+\includegraphics[width=18cm]{kinetic_stats_opt.pdf}
 \hfill{}
@@
 In fact, it is easier for VacTH to fit magnetic probes than flux loops
-% while magnetic probes do not fully determine the magnetic flux. 
-% This is also apparent in $E_\mathrm{mp}$ and $E_\mathrm{fl}$ values in Tables \ref{table:ex4275} and \ref{table:ex6962}. 
 An additional optimization of the fitting weights or algorithm is probably needed.
@@
 \hfill{}
-\includegraphics[width=8cm]{figures/convergence_ratio_6962.pdf}
+\includegraphics[width=8cm]{convergence_ratio_6962.pdf}
 \hfill{}

### 2015-06-03 review1/response.txt
Response to review (first version, TO BE CHECKED)

Dear editors, dear referee,

thank you for your valuable comments concerning our manuscript. We have addressed all of them and corrected the text accordingly. Please find detailed answers below.

Best regards,
Jakub Urban

> Reviewer #2: The manuscript is well organized and written in general. I found some misprints and other small inconsistencies to check for the final version. I have also some comments.
> Misprints.
> 1. Introduction. 
> now: … which predicts PF coils currents from a give plasma boundary and profiles.
> to be: … which predicts PF coils currents from a given plasma boundary and profiles.
> 3.2 Statistical analysis
> now: For shot 6962, equilibria with TS pressure profiles and with linear p' and FF'.
> to be: For shot 6962, equilibria with TS pressure profiles and with linear p' and FF' is used.
> 3.2 Statistical analysis
> now: We can observer that the…
> to be: We can observe that the…

All the misprints have been corrected.

> Inconsistencies.
> 
> 2. Verification and validation procedure.
> When defining verification and validation procedure you specify 4 steps. Then you expain them, but in explanation you change order:
> Procedure definition:
> 4. Reconstruct FREEBIE equilibria using EFIT++ and VacTH with various parameters and artificial input noise.
> Later in text:
> In the optional third step, an artificial random noise is added to the calculated values of Ip, magnetic probes and flux loops.

We have changed the text of chapter 2:
" ...
FREEBIE inputs can be modified in the optional third step. In the following analysis, we particularly use realistic pressure profiles, estimated by Thomson scattering diagnostics.

The final fourth step consists of reconstructing the equilibria form synthetic FREEBIE data using EFIT++ and VacTH. An artificial random noise is added to the calculated values of $I_\mathrm{p}$, magnetic probes and flux loops. In particular, for a given noise level $\epsilon$, $\tilde X = \left( {1 + U\left( { - \epsilon, \epsilon} \right)^\mathrm{T}} \right)X$, where $X$ is a row vector of the synthetic diagnostics data and $U\left( { - \epsilon, \epsilon} \right)$ is a random vector of the same shape as $X$ with a uniform distribution on $\left( { - \epsilon, \epsilon} \right)$. The reconstructions are then compared to the original equilibrium, focusing on global parameters and geometry. Scans are performed over noise levels ($\epsilon$) and selected code parameters: $p'$ and $FF'$ polynomial degrees in EFIT++ ($n_{p'}$, $n_{FF'}$) and the number of harmonics ($n_P$, $n_Q$) in VacTH. The following quantities are used for the comparison.
... "

> 3. Results.
> You introduce different shapes as circular elongated and diverted. Then in 3.1 you are using term 'eliptical' several times, that can refer to both elongated and diverted plasmas. Could you specify which plasmas you refer to in each case.

We now use 'elliptical' throughout the paper when referring to elongated, limited plasmas. In the beginning of chapter 3, we now explicitly say: "These cases include circular, elliptical (limited) and diverted plasmas with different currents." We believe that this avoids any confusion since diverted plasmas are always designated explicitly.

> Comments.
> 
> 1. When talking about ITM CPOs, I think you need reference to explain what is it. It could be for example:
> G. Manduchi et al, Fusion Eng. Design 83 (2008) 462

The reference has been added.

> 2. Annotation to Fig.2. Last sentence is not clear for me, what do you mean? Have you artificially scattered zero error data? Could you explain this?

We simply scattered the x position of the data points with zero input error in order to suppress their overlap. We have removed this sentence from the caption as it should be clear enough that the error of these data points is zero. Based on your comment, the sentence was a bit confusing.

> 3. Fig.2. I propose to change color for case s3 from purple to (for example) green to distinguish results (it is hard to do now).

The colour has been changed.

> 4. Conclusions. When you are saying that VacTH is a promising tool for a real-feedback control, on what reasoning are you relying? In the text it is shown that VacTH is able to reconstruct plasma surface with 'reasonable' accuracy. I think in order to conclude about it's applicability for real-time control it should be verified against another real-time tools. My conclusion from the results shown is that further improvements in the code are needed to make it more robust (that is required for real-time feedback control).

The conclusion we draw in the paper is that VacTH is promising for real-time shape control. In out opinion, the accuracy of VacTH shape reconstruction shall be reasonable for real time plasma position/shape control. However, we agree that the robustness (and the accuracy as well) should be improved. There are actually new results for VacTH parameters optimizations. We do not think that VacTH must necessarily be compared to other real-time shape reconstruction tools providing that it shows enough accuracy, robustness and speed required by a particular feed-back algorithm. Since such an algorithm does not exist yet on COMPASS, we do not have absolute measures.
We have extended the last sentence of the conclusions: "We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape, although its robustness and accuracy should be improved."

### 2015-06-03 Conclusions.tex
submitted version: * no subdirectories * removed comments * added cover letter and research highlights
Response to review (first version, TO BE CHECKED)

--- 2014-09-11 Conclusions.tex
@@
 FREEBIE model equilibria, either with linear $p'$ and $FF'$ profiles or with pressure profiles from Thomson scattering diagnostic, then served to assess the credibility of EFIT++ reconstructions.
-% This has not been up to now possible.
-
-We show that magnetic reconstruction EFIT++ with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape reconstruction but introduces a systematic error in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$.
-The reconstruction properties can be significantly improved by using quadratic $p'$ for diverted plasmas, which removes the systematic error and also improves the LCFS reconstruction.
+Magnetic EFIT++ reconstruction with linear $p'$ and $FF'$ features a relatively good accuracy of 1 -- 2 cm in the plasma shape but introduces systematic errors both in the shape and in internal plasma parameters, such as $W$, $l_{\mathrm i}$, $\beta_{\mathrm p}$ or $q_0$.
+The reconstruction properties can be significantly improved by using quadratic $p'$ for elliptical and divertor plasmas, which removes the systematic error and also improves the LCFS reconstruction.
 EFIT++ converges in 100~\% cases in this regime.
-
 Optimum parameters for VacTH have been estimated.
 In particular, the optimum number of harmonics is 4 otherwise VacTH fails to converge in many cases, even without any input error.
-16 flux loops and only 8 magnetic must be used as VacTH input.
+16 flux loops and only 8 magnetic probes must be used as VacTH input.
 With less flux loops or more magnetic probes the code performs significantly worse.
-We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape.
+We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape, although its robustness and accuracy should be improved.
 

### 2015-06-03 Procedure.tex
Response to review (first version, TO BE CHECKED)

@@
 It should be noted here that to set up a free-boundary equilibrium code, a rather complete machine description is necessary (in particular, the PF coils geometry and circuits, limiter, vessel and other passive PF elements and magnetic diagnostics configuration).
-We adopted the description that was already available for EFIT++ and transformed it to ITM CPO's (Integrated Tokamak Modelling Consistent Physical Objects) structures, which are subsequently either used directly in FREEBIE or converted to VacTH specific input format.
+We adopted the description that was already available for EFIT++ and transformed it to ITM CPO's (Integrated Tokamak Modelling Consistent Physical Objects \cite{Manduchi2008}) structures, which are subsequently either used directly in FREEBIE or converted to VacTH specific input format.
 
@@
 
-In the optional third step, an artificial random noise is added to the calculated values of $I_\mathrm{p}$, magnetic probes and flux loops.
-In particular, for a given noise level $\epsilon$, $\tilde X = \left( {1 + U\left( { - \epsilon, \epsilon} \right)^\mathrm{T}} \right)X$, where $X$ is a row vector of the synthetic diagnostics data and $U\left( { - \epsilon, \epsilon} \right)$ is a random vector of the same shape as $X$ with a uniform distribution on $\left( { - \epsilon, \epsilon} \right)$.
+FREEBIE inputs can be modified in the optional third step. In the following analysis, we particularly use realistic pressure profiles, estimated by Thomson scattering diagnostics.
 
 The final fourth step consists of reconstructing the equilibria form synthetic FREEBIE data using EFIT++ and VacTH. 
+An artificial random noise is added to the calculated values of $I_\mathrm{p}$, magnetic probes and flux loops.
+In particular, for a given noise level $\epsilon$, $\tilde X = \left( {1 + U\left( { - \epsilon, \epsilon} \right)^\mathrm{T}} \right)X$, where $X$ is a row vector of the synthetic diagnostics data and $U\left( { - \epsilon, \epsilon} \right)$ is a random vector of the same shape as $X$ with a uniform distribution on $\left( { - \epsilon, \epsilon} \right)$.
 The reconstructions are then compared to the original equilibrium, focusing on global parameters and geometry.

### 2015-06-03 Results.tex
Response to review (first version, TO BE CHECKED)

@@
 \hfill{}
-\includegraphics[width=18cm]{example_6962.pdf}
+\includegraphics[width=17.5cm]{example_6962.pdf}
 \hfill{}
@@
 
-We have selected five time slices from COMPAS shots 4275 and 6962 (i.e. 10 cases in total) for the analysis. These cases include circular, elongated and diverted plasmas with different currents.
+We have selected five time slices from COMPAS shots 4275 and 6962 (i.e.
+10 cases in total) for the analysis.
+These cases include circular, elliptical (limited) and diverted plasmas with different currents.
 
@@
 \hfill{}
-\includegraphics[width=18cm]{RZstats.pdf}
+\includegraphics[width=17.5cm]{RZstats.pdf}
 \hfill{}
@@
 Input error is calculated as an average of $I_{\rm{p}}$, magnetic probes and flux loops values.
-Zero input error data are scattered for a better visibility.}
+% Zero input error data are scattered for a better visibility.
+}
 \label{fig:RZstats}
@@
 \hfill{}
-\includegraphics[width=18cm]{kinetic_stats_opt.pdf}
+\includegraphics[width=17.5cm]{kinetic_stats_opt.pdf}
 \hfill{}
@@
 The same cases as above (time slices of shots 4275 and 6962) are used as target equilibria.
-For shot 6962, equilibria with TS pressure profiles and with linear $p'$ and $FF'$.
+For shot 6962, equilibria with TS pressure profiles and with linear $p'$ and $FF'$ are used.
 This means there is 15 different target equilibria in total.
@@
 \ref{fig:RZstats}.
-We can observer that the LCFS reconstructed with EFIT++ for target linear $p'$ and $FF'$ profiles (selection 1) are within 1~cm errors.
+We can observe that the LCFS reconstructed with EFIT++ for target linear $p'$ and $FF'$ profiles (selection 1) are within 1~cm errors.
 There are, however, cases with up to 3 cm errors in $Z_{\rm{min}}$ for the more realistic TS pressure profiles (selection 2) if $n_{p'}=1$ is used.
@@
 It is known that magnetic reconstruction with EFIT is difficult for small circular plasmas (without additional constraints, particularly the stored energy) \cite{efit1985}.
-This suggests that using $n_{p'}=1$ for circular plasmas and $n_{p'}=2$ for elongated and diverted plasmas might lead to better results.
+This suggests that using $n_{p'}=1$ for circular plasmas and $n_{p'}=2$ for elliptical and diverted plasmas might lead to better results.
 This is demonstrated in the bottom row of Fig.

### 2015-06-04 review1/response.txt
Added list of changes to the response.

@@
 
-The colour has been changed.
+The colour has been changed to green.
 
@@
 The conclusion we draw in the paper is that VacTH is promising for real-time shape control.
-In out opinion, the accuracy of VacTH shape reconstruction shall be reasonable for real time plasma position/shape control.
+In our opinion, the accuracy of VacTH shape reconstruction shall be reasonable for real time plasma position/shape control.
 However, we agree that the robustness (and the accuracy as well) should be improved.
@@
 We have extended the last sentence of the conclusions: "We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape, although its robustness and accuracy should be improved."
+
+Additional amendments to the manuscript:
+1. VacTH reference updated in abstract to "[B. Faugeras et al., PPCF 2014, 114010]".
+2. Figures in the Results chapter have been scaled down to 97 % in order to fit the longer reference list.
+3. A grammatical error has been corrected: "For shot 6962, equilibria with TS pressure profiles and with linear $p'$ and $FF'$ are used." ("are used" was missing in the original text.)
+4. Paragraphs are no longer used in Conclusions in order to save space.

### 2015-06-12 review1/response.txt
slightly revised conclusion, RESPONSE SUBMITTED

@@
 
-thank you for your valuable comments concerning our manuscript. We have addressed all of them and corrected the text accordingly. Please find detailed answers below.
+thank you for your valuable comments concerning our manuscript. We have addressed all of them and amended the text accordingly. Please find detailed answers below.
 
 Best regards,
-Jakub Urban
+Jakub Urban et al.
 
@@
 Since such an algorithm does not exist yet on COMPASS, we do not have absolute measures.
-We have extended the last sentence of the conclusions: "We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape, although its robustness and accuracy should be improved."
+We have extended the last sentence of the conclusions: "We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape.We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape.
+We will further improve its robustness and accuracy and test the code within a suitable feedback algorithm."
 

### 2015-06-12 Conclusions.tex
slightly revised conclusion, RESPONSE SUBMITTED

@@
 With less flux loops or more magnetic probes the code performs significantly worse.
-We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape, although its robustness and accuracy should be improved.
+We conclude that VacTH is a promising tool pertinent for a real-time feedback control of the plasma shape.
+We will further improve its robustness and accuracy and test the code within a suitable feedback algorithm.
 
